ICS_HC

### 2019-06-17 ICS_HC.Rmd
updating to reflect that new export was combined with old in Cleaning script

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4a<-read.csv("ICS_CD4_clean.csv")
cd4b<-read.csv("ICS_CD4_new.csv")

CD4<-plot_filter(read.csv("ICS_CD4_Cytokine_clean.csv"))
CD4b<-plot_filter(read.csv("ICS_CD4_Cytokine_new.csv"))

phen<-read.csv("ICS_CD4_Phenotyping_clean.csv")
phenb<-read.csv("ICS_CD4_phenotype_new_clean.csv")
```

@@

```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(cd4a, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4a, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

```{r, fig.height=3, fig.width=6}
colnames<-names(dplyr::select(cd4b, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4b, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

@@

```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(CD4b, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(CD4b, Stim=="PMA")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

@@

#Phenotype from PMA
```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(phenb, -X.1, -X, -id, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(phenb, Stim=="PMA")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

```{r}
colnames<-names(dplyr::select(phen, -X, -X.1, -id, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(phen, phen$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col) 
    print(b)
    c<-plot_with_all_stats(a, "PEP", col)+labs(y=col)
    print(c)
     #will return the output for each character string in the loop
}

colnames<-names(dplyr::select(phenb, -X, -X.1, -id, -Sample, -Donor, -Stim, -TB, -SM))
for(col in colnames){#this will loop through each character string in the list
    a<-subset(phenb, phenb$Stim=="PEP") #subsets the data to only contain the unstimulated samples
    #inserts each character string into the column argument of the pvals function written above
    b<-pvals_6(a, col) 
    print(b)
    c<-plot_with_all_stats(a, "PEP", col)+labs(y=col)
    print(c)
    #will return the output for each character string in the loop
}
```

>>>>

```{r}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
cd4<-read.csv("ICS_CD4_clean.csv")

CD4<-plot_filter(read.csv("ICS_CD4_Cytokine_clean.csv"))

phen<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
```

@@

```{r, fig.height=3, fig.width=6}
library(knitr)
colnames<-names(dplyr::select(cd4, -X, -Sample, -Donor, -Stim, -TB, -SM))
df<-filter(cd4, Stim=="UN")
df<-mutate_hc(df)
for(col in colnames){
    print(col)
    print(pvals_hc(df, col))
    grid.arrange(
       plot_hc(df[df$QFT=="QFT-",], "SM", col)+labs(title="QFT- Only"), 
       plot_hc(df, "SM", col)+labs(title="All Healthy Controls"),
       ncol=2
    )
}
```

@@

@@

##Actual analysis
